---
title: "AZ Trends in AGB"
author: "Eric R. Scott"
format: 
  html:
    code-fold: true
editor: visual
---

```{r}
#| label: setup
#| warning: false
#| message: false

library(targets)
library(here)
library(tidyterra)
library(ggplot2)
library(purrr)
library(ragg)
library(ggridges)
library(ggdist)

tar_load(starts_with("slope"), store = here("_targets"))

```

```{r}
#| label: wrangle

df <- 
  list(`Xu et al.` = slope_xu_agb_xu_agb,
       `Liu et al.` = slope_liu_agb_liu_agb, 
       `chopping` = slope_chopping_agb_chopping_agb) |> 
  purrr::map(\(x) {
    x[["slope"]] |> as_tibble(na.rm = TRUE)
  }) |> 
  list_rbind(names_to = "product")

```

Visualizing the distribution of values among these datasets is tricky for two reasons:

1.  Their resolution and therefore sample size varies by several orders of magnitude.
2.  In some products, the most common slope *by far* is 0.

```{r}
df |> count(product)
```

```{r}
df |> 
  group_by(product) |> 
  summarize(`% slopes = 0` = sum(slope == 0)/dplyr::n() *100)

df |> 
  group_by(product) |> 
  summarize(`% slopes near 0` = sum(dplyr::near(slope, 0, tol = 0.01)/dplyr::n())*100)
```

## Boxplots

Standard boxplots are probably not a good fit since any values outside of 1.5 \* IQR are "outliers" and because there are so many data points, a lot are "outliers"

```{r}
p <- ggplot(df, aes(x = slope, y = product)) + labs(x = "∆Mg/Ha/yr")

p + geom_boxplot()
```

You can remove "outliers", but I'm not sure that's the best idea.
Chopping et al. has so many points, that it looks like all non-zero points are "outliers".

```{r}
p + geom_boxplot(outliers = FALSE)
```

## Violin plots / Density plots

These don't look great because even if you were to add lines for median and IQR, you wouldn't be able to see them.

```{r}
p + geom_violin()
```

```{r}
p + geom_density_ridges()
```

## Point interval

A point interval plot from `ggdist` shows the median (point) and different intervals.
Here I'm showing the range of the 80th percentile (fattest line), and 95th percentile of data (thinnest line).
These quantiles are arbitrary and can be changed (both what quantiles and how many).

```{r}
p + stat_pointinterval(.width = c(.8, .95))
```
