---
title: "AZ Trends in AGB"
author: "Eric R. Scott"
format: 
  html:
    code-fold: true
editor: visual
---

```{r}
#| label: setup
#| warning: false
#| message: false

library(targets)
library(here)
library(terra)
library(tidyterra)
library(purrr)
library(dplyr)
library(ggplot2)
library(ragg)
library(ggtext)

tar_load(c(slope_liu_agb, slope_chopping_agb, slope_xu_agb), store = here("_targets"))

df <- 
  map(c("Liu et al." = slope_liu_agb,
        "Chopping et al." = slope_chopping_agb,
        "Xu et al." = slope_xu_agb), 
      \(x) as_tibble(x, na.rm = TRUE) |> select(-p.value)) |> 
  list_rbind(names_to = "product")
df

theme_set(theme_minimal(base_family = "sans"))
```

Visualizing the distribution of values among these datasets is tricky for two reasons:

1.  Their resolution and therefore sample size varies by several orders of magnitude. E.g. the LT-GNN dataset (not shown) has tens of millions of values and the Liu et al. dataset has 492.
2.  In some products, the most common slope *by far* is 0.

```{r}
df |> count(product)
```

```{r}
df |> 
  group_by(product) |> 
  summarize(`% slopes = 0` = sum(slope == 0)/dplyr::n() *100)

df |> 
  group_by(product) |> 
  summarize(`% slopes near 0` = sum(dplyr::near(slope, 0, tol = 0.01)/dplyr::n())*100)
```

## Boxplots

Standard boxplots are probably not a good fit since any values outside of 1.5 \* IQR are "outliers" and because there are so many data points, a lot are "outliers"

```{r}
p <- ggplot(df, aes(x = slope, y = product)) + labs(x = "∆Mg/Ha/yr")

p + geom_boxplot()
```

You can remove "outliers", but I'm not sure that's the best idea. Chopping et al. has so many points, that it looks like all non-zero points are "outliers".

```{r}
p + geom_boxplot(outliers = FALSE)
```

## Violin plots

These don't look great because even if you were to add lines for median and IQR, you wouldn't be able to see them.

```{r}
p + geom_violin()
```

## Point interval

This is what I settled on for now. The points show the median data value, the thick lines show the IQR (25th and 75th percentiles) and the thin lines show the middle 80% of data (10th and 90th percentiles). The vertical dashed line just shows where 0 is.

```{r}
tar_read(summary_plot, store = here("_targets"))
```
